\large \textbf{Burrows-Wheeler transform for terabases}

### 2015-11-04 paper/paper.tex
References; link to arXiv version of the paper.

The most straightforward approach to \BWT{} construction is to build a \emph{suffix array} for the sequences using a fast general-purpose algorithm \cite{Mori2008,Nong2011}. Given the sequences and their suffix array, we can easily build the \BWT{} of the sequences. These algorithms cannot be used with large datasets, as they require several times more memory than the sequences themselves. Suffix arrays can be built on disk \cite{Gonnet1992}, but even the fastest algorithms cannot index the data faster than 1\nobreakdash--2~Mbp/s \cite{Bingmann2013,Kaerkkaeinen2014a,Nong2014,Kaerkkaeinen2015a}.

>>>>

The most straightforward approach to \BWT{} construction is to build a \emph{suffix array} for the sequences using a fast general-purpose algorithm \cite{Mori2008,Nong2011}. Given the sequences and their suffix array, we can easily build the \BWT{} of the sequences. These algorithms cannot be used with large datasets, as they require several times more memory than the sequences themselves. Suffix arrays can be built on disk \cite{Gonnet1992}, but even the fastest algorithms cannot index the data faster than 1\nobreakdash--2~Mbp/s \cite{Bingmann2013,Kaerkkaeinen2014a,Nong2014,Nong2015,Kaerkkaeinen2015a,Liu2015a}.
